### 2018-07-25 express2018/conclusions.tex
Merged changes of 'conclusions.tex'

% \section{To Do}
% \label{s:todo}

% \finish{discuss multiple equations/contractions}

% The formalisation of multi-variable context (or expressions) and the version of
% ``unique solutions'' theorems with multiple equations/contractions, is
% a relative hard problem. To the best of our knowledge, so far there's no formalization (in any kind of
% process calculi) touching these areas yet. However, we've made a few initial steps
% of this interesting problem.

@@

For the future work, it would be worth extending the current work
to multi-variable equations/contractions. \hl{
A the key aspect could be using unguarded constants as free variables
(\texttt{FV}) and define guardness directly on type CCS (instead of CCS
$\rightarrow$ CCS):}
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{weakly_guarded1} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X}. \HOLBoundVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{e} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \HOLBoundVar{e}
\end{alltt}

Formalising other equivalences and preorders could also be considered,
notably the trace equivalences as well as 
more refined calculi such as  value-passing CCS (e.g.,  exploiting the type variable
of actions).}

On another line, one could examine the formalisation of a different
approach \cite{DurierHS17} to unique
solutions, in which the use of contraction is
replaced by semantic conditions on process transitions such as
divergence. 
% Further plan on the formalisation mainly includes: 1) the extension to
% multi-variable equation/contractions. 2) the support of recursion
% operators in 
% CCS context and expressions.

@@

We have benefitted from suggestions and comments 
from several people from the HOL
community, including Robert Beers, Jeremy Dawson,
Ramana Kumar,
Michael Norrish, 
Konrad Slind, and
Thomas Tuerk.
%
The second half of this
paper was written in memory of Mike J. Gordon, the creator of HOL theorem prover.

>>>>

%%%% -*- Mode: LaTeX -*-

@@

For the future work, it would be worth extending the current work
to multi-variable equations/contractions. \hl{Preliminary work shows that,
a key aspect could be using unguarded constants as free variables
(\texttt{FV}) and define guardness directly on type CCS (instead of CCS
$\rightarrow$ CCS) then connect to previous context:}
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{weakly_guarded1} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X}. \HOLBoundVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{e} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \HOLBoundVar{e}
\end{alltt}

Formalising other equivalences and preorders could also be considered,
notably the trace equivalences, \hl{as well as more refined process
calculi such as value-passing CCS (e.g.~ exploiting the type variable
of actions).}
%
On another research line, one could examine the formalisation of a different
approach \cite{DurierHS17} to unique
solutions, in which the use of contraction is
replaced by semantic conditions on process transitions such as
divergence.

% Further plan on the formalisation mainly includes: 1) the extension to
% multi-variable equation/contractions. 2) the support of recursion
% operators in 
% CCS context and expressions.

@@

We have benefitted from suggestions and comments 
from several people from the HOL
community, including (in alphabet order) Robert Beers, Jeremy Dawson,
Ramana Kumar,
Michael Norrish, 
Konrad Slind, and
Thomas Tuerk.
%
The second half of this
paper was written in memory of Mike J. Gordon, the creator of HOL theorem prover.
